Comparing Predicted Boundaries vs Called Boundaries

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
changed color to forest green

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
    facet_grid(~ Annotation) +    
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list(c("PBNC", "CAP"),
                                   c("PBNC", "CBNP"),
                                   c("CBNP", "CAP")),
                vjust = 0,
                textsize = 4,
                size = .5,
                step_increase = .08,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to Annotation")+
    xlab("") +
    scale_fill_manual(name="Boundary Region",
                      values=c("green",
                               "red",
                               "blue"))+
    scale_color_manual(values=c("green",
                               "red",
                               "blue")) +
    guides(color=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```

>>>>

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
    facet_grid(~ Annotation) +    
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list(c("PBNC", "CAP"),
                                   c("PBNC", "CBNP"),
                                   c("CBNP", "CAP")),
                vjust = 0,
                textsize = 4,
                size = .5,
                step_increase = .08,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to Annotation")+
    xlab("") +
    scale_fill_manual(name="Boundary Region",
                      values=c("forestgreen",
                               "red",
                               "blue"))+
    scale_color_manual(values=c("forestgreen",
                               "red",
                               "blue")) +
    guides(color=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```
